A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-28 notes/notes.tex
completed the bethe lattice part

\documentclass{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

@@

 The full Hamiltonian reads
\begin{equation}\begin{aligned}
	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
	=& -\frac{1}{2}\left(Uw - 2U_b\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
\end{aligned}\end{equation}
The bulk model hence obtained is again a Hubbard-Heisenberg model. In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\). In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w\):
\begin{equation}\begin{aligned}
	\label{2siam_to_hubb}
	H_\text{full} &= \frac{1}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{1}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
		      &= -\left(U/2 - U_b/w\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{2w-4}t + t/w - 4V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
\end{aligned}\end{equation}
The mappings between the parameters of the auxiliary model and the bulk are
\begin{equation}\begin{aligned}
	t_\text{H-H} = \left(\frac{N}{2w-4}t + t/w - 4V/w\right),~ ~ ~ U_\text{H-H} = \left(U/2 - U_b/w\right),~ ~ ~ J_\text{H-H} = 4J/w
\end{aligned}\end{equation}

\section{Single-particle Green's function}
We now define the Greens function {\it operators}:
\begin{equation}\begin{aligned}
	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
\end{aligned}\end{equation}
Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\). While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\). This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
\begin{equation}\begin{aligned}
\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
\end{aligned}\end{equation}
We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model. Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate. We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
\end{aligned}\end{equation}
The superscript \(p\) indicates that this is the particle propagation matrix element. Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters. Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\). There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\). Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent. These configurations are shown in fig.~\ref{diag_conrib}.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
	\label{diag_conrib}
\end{figure}

\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
\end{aligned}\end{equation}
where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\). We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\). \(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.

By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
\end{aligned}\end{equation}
There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\). We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\). The hole propagation matrix element can be obtained similarly:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
\end{aligned}\end{equation}
where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).

The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
\begin{itemize}
	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). We can symmetrise it by exchanging \(d_1\) and \(d_2\): 
	\begin{equation}\begin{aligned}
		\frac{1}{2}\left[\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} + \braket{\Phi_0 | c_{d_2\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}\right] = \frac{1}{2}\sum_{n} \left(\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{2,n}\right)^* d^p_{1,n}\right) \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{aligned}\end{equation}
	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
	\begin{equation}
		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{equation}
		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
	\begin{equation}
		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{1}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{equation}
\end{itemize}
These choices are shown in fig.~\ref{off-diag-contrib}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
	\label{off-diag-contrib}
\end{figure}

Adding all contributions gives
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
\end{aligned}\end{equation}
The hole counterpart is
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
\end{aligned}\end{equation}
where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).

\par\noindent
\begin{minipage}{0.65\textwidth}
	The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\). This is shown in fig.~\ref{next-near}. In other words, the two sites have to form the two most separated vertices of a right-angled triangle. To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\). We can set \(A=d_1, C=0_2\). The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\). This gives two configurations. Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\). These four configurations are shown in fig.~\ref{nn-configs}. 
\end{minipage}
\hspace*{\fill}
\begin{minipage}{0.29\textwidth}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/next-near.pdf}
	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
	\label{next-near}
\end{minipage}

@@

In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
\begin{gather}
\label{green_eq_final_siam}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
\end{gather}

>>>>

\documentclass[10pt]{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

@@

 The full Hamiltonian reads
\begin{equation}\begin{aligned}
	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
\end{aligned}\end{equation}
The bulk model hence obtained is again a Hubbard-Heisenberg model. In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\). In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
\begin{equation}\begin{aligned}
	\label{2siam_to_hubb}
	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
\end{aligned}\end{equation}
The mappings between the parameters of the auxiliary model and the bulk are
\begin{equation}\begin{aligned}
	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
\end{aligned}\end{equation}

\section{Single-particle Green's function}
We now define the Greens function {\it operators}:
\begin{equation}\begin{aligned}
	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
\end{aligned}\end{equation}
Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\). While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
\begin{equation}\begin{aligned}
	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
\end{aligned}\end{equation}
This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
\begin{equation}\begin{aligned}
\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
\end{aligned}\end{equation}
We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model. Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate. We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
\end{aligned}\end{equation}
The superscript \(p\) indicates that this is the particle propagation matrix element. Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters. Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\). There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\). Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent. These configurations are shown in fig.~\ref{diag_conrib}.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
	\label{diag_conrib}
\end{figure}

\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
\end{aligned}\end{equation}
where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\). We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\). \(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.

By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
\end{aligned}\end{equation}
There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\). We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\). The hole propagation matrix element can be obtained similarly:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
\end{aligned}\end{equation}
where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).

The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
\begin{itemize}
	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
	\begin{equation}\begin{aligned}
		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{aligned}\end{equation}
	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
	\begin{equation}
		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{equation}
		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
	\begin{equation}
		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
	\end{equation}
\end{itemize}
These choices are shown in fig.~\ref{off-diag-contrib}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
	\label{off-diag-contrib}
\end{figure}

Adding all contributions gives
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
\end{aligned}\end{equation}
The hole counterpart is
\begin{equation}\begin{aligned}
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
\end{aligned}\end{equation}
where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).

The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\). This is shown in fig.~\ref{next-near}.

\par\noindent
\begin{minipage}{0.6\textwidth}
The essence is that the two sites have to form the two most separated vertices of a right-angled triangle. To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\). We can set \(A=d_1, C=0_2\). The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\). Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\). These four configurations are shown in fig.~\ref{nn-configs}. 
\end{minipage}
\hspace*{\fill}
\begin{minipage}{0.35\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
	\label{next-near}
\end{minipage}

@@

In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
\begin{gather}
\label{green_eq_final_siam}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
\end{gather}
